### 2022-07-14 Journal1/Response3/Response.tex

\begin{document}
%\vspace*{-10ex}
%\sloppy
\maketitle
We would like to thank the editor and reviewers for their constructive comments on our manuscript. They have been beneficial in revising this paper, and we have improved the technical content and presentation quality through their assistance. We greatly appreciate their generous help. In addition, we would like to acknowledge the assistance of Dr. Onel Luis Alcaraz López in this revision.
Moreover, we have reviewed and incorporated all the comments and suggestions.
Additionally, we removed two figures of Fig. 2 and Fig. 3 since they don't add much to what is already written in words after revision. Even after this revision (comment 2 of reviewer 3), Fig. 2 makes the paper vaguer. We also aim for a more concise manuscript.
We hope that the modifications we have made to the manuscript and the responses we have provided herein will alleviate the reviewers' concerns. Below, please find our detailed responses to the editor and reviewers' comments and suggestions.
\\ [-3.ex]
% % % % % % % % % % % % % % % Editor % % % % % % % % % % % % % % % % % % % %

\clearpage
\noindent
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Editor} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent  Comments to the Author} ``I think the paper should undergo a major revision. It is important to take special attention to the comments of reviewer 2.''\\
\hline
\end{longtable}

\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the Editor for his comments and for giving us this opportunity to improve our paper. We used the comments to improve our paper and eliminate problems. We are confident that we were able to address the reviewers’ and Editor’s suggestions.
We upload our point-by-point response to the comments (below) (response to reviewers) and the updated manuscript.

@@

%\begin{longtable}{|p{0.975\textwidth}|}
%\hline \hline
%\RaggedRight
%\cellcolor{green!10}
%[1] F. Patolsky, B. P. Timko, G. Yu, Y. Fang, A. B. Greytak, G. Zheng, and C. M. Lieber, ``Detection, stimulation, and inhibition of neuronal signals with high-density nanowire transistor arrays,'' Science, vol. 313, no. 5790, pp. 1100-1104, 2006.
%\\
%\hline
%\end{longtable}

% % % % % % % % % % % % % % % Reviewer 1 % % % % % % % % % % % % % % % % % % % %
\clearpage
\noindent
\begin{longtable}{|p{.975\textwidth}|}
\hline \hline %\hline \hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Reviewer 1} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent Comments to the Author} ``
The authors have addressed the comments provided in a previous review. The contributions are clear and the results are compared to some related work, so the reader can somewhat contextualize the proposed solution. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the reviewer for the careful and thorough reading of this manuscript. We hope that the responses provided herein can satisfy the reviewer's concerns.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment1:} ``However, the paper still needs some improvement in terms of readability. Some paragraphs are too long  ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We revised the whole paper and checked the text entirely according to this comment. For instance, the introduction has been rewritten totally. We also revised the system model, proposed algorithms, and shortened long paragraphs based on this comment. Moreover, we shortened the numerical results and feasible region section and modified the conclusion section. 
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment2:} `` the figures are difficult to locate from their reference in the text (figures at top, as typical IEEE template is better), the text in the figures is too small ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
Thank you for this comment. We think that these changes improve the readability of the manuscripts.
 We modified all the paper's figures entirely concerning this comment and located them in sub-figures to make them more determined. Moreover, we modified whole the figures and made the texts larger and more readable. 
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment3:} ``the contributions discussed in the introduction are not easily found in the other parts of the paper.  ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We thank the reviewer for asking us to add clarity to our paper and reducing ambiguity in this condition. We changed the contribution in a better way based on this comment. We have removed some sentences and rewritten the contributions in the same order as our paper's section.
We explained it in the system model, proposed algorithm, and numerical results.
Below we report the whole contribution section.

@@

% % % % % % % % % % % % % % % Reviewer 2 % % % % % % % % % % % % % % % % % % % %
\clearpage
\noindent
\begin{longtable}{|p{.975\textwidth}|}
\hline \hline %\hline \hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Reviewer 2} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent Comments to the Author} ``
The Reviewer would like to thank the authors for their revision of the paper with respect to the comments and suggestions in the previous submission. Whereas the authors have considered parts of the suggestions and improved specific areas of the work, there are still a lot of remaining issues of concern in the current version of the paper. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
It is our pleasure to thank the reviewer for the careful reading of this manuscript, providing thoughtful comments, and offering constructive suggestions that strengthened and enhanced its quality. 
We hope that the responses provided herein can relieve the reviewer’s concerns.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment1:} ``While the authors have taken into consideration the Reviewer’s comments about the re-structuring of the Introduction, I am afraid that the current version is not in the adequate state for publication. Initially, the paragraphs of the Introduction have no logical connection among them. It seems that until the Related Literature subsection all paragraphs are disconnected and only introduce concepts. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
In response to the reviewer's suggestions, we modified the introduction completely. Using this comment as a guide, we attempted to have a logical connection between paragraphs. The final version of the 'Introduction' Section is reported below.

@@

Table I lists the acronyms used throughout this paper, which is organized as follows.
Relevant literature related to our work is discussed in Section II, while Section III briefly overviews the O-RAN architecture.
The system model and the problem formulation are described in Section IV, V, respectively. The details of our proposed resource management algorithm are introduced in Section VI. In Section VII, numerical results are provided to evaluate the performance of the proposed algorithm. Finally, Section VIII concludes the paper.

 \vspace*{-2em}
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment2:} `` Moreover, I find the ORAN explanation in the Introduction very lengthy and unnecessary. I would definitely suggest to move that as a background Section. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would appreciate your comments to enhance and clarify this paper section. We updated the manuscript by moving the ORAN explanation as a background section in Section III and modifying it to present it better.
We also emphasized the importance of this section based on this comment. 
Below we report it.

@@

O-RAN is an appropriate alternative to the next generation of radio access networks due to its flexibility, openness, low operational costs, and intelligence. O-RAN was developed to jointly benefit from the advantages of virtual RAN (vRAN) and cloud RAN (C-RAN). With RAN virtualization, operators can improve flexibility, reduce capital expenditures (CAPEX) and operating expenses (OPEX), and add new capabilities to the network more quickly. The C-RAN architecture divides the RAN into two major parts: the radio remote head (RRH) and the baseband unit (BBU). Several distributed RRHs can be connected to a centralized BBU, called BBU-pool [27]. Unlike C-RAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
 Most real-time baseband processing is performed in the O-DU layer, while non-real-time baseband processing is mostly executed in the O-CU layer.

In the O-RAN architecture, the PHY is divided into low and high PHY, unlike C-RAN. As shown in Fig. 1, O-RU is a logical node that contains RF and low PHY. The former transmits or receives radio signals, while the latter includes digital beamforming. Typically, the O-DU constitutes a logical node with high PHY, MAC, and RLC. It contains a subfunction of the eNodeB and is deployed near the O-RU.
Moreover, O-DU is connected to an O-RU with an open fronthaul interface.
In addition to supporting the lower layers of the protocol stack, O-CU also provides support for the higher layers.
The O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). The former hosts the packet data convergence protocol (PDCP)-UP and the service data adaption protocol (SDAP), while the latter hosts PDCP-CP and radio resource control (RRC).
O-DU and O-CU are connected via an open and well-defined interface $\text{F}_1$.
The O-RAN architecture contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud. Orchestration and Automation include functions such as RIC Non-Real-Time. RIC is responsible for machine learning methods and making the system more intelligent  [10]–[12], [28]–[31].
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment3:} `` Furthermore, it is surprising how the Introduction does not contain a single research challenge. Why is the problem relevant at all? Why do you even need to study this problem and why is it hard to solve? ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We agree with the reviewer that explaining the research challenges is of value to allow the reader to understand the difficulties encountered in proposing the submitted work. For this reason, 
we added the motivation subsection in Section I-B and answered these questions. We rewrite it as follows.

@@

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment5:} `` In a similar fashion, the authors have not considered the Reviewer’s suggestion to move the Related Work as a separate Section in order to improve the flow and clarity of the Introduction. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We apologize for not considering this comment correctly in the previous version.
We thank the reviewer for clarifying this comment for us. We moved the related works to Section II and modified it as below.

@@

Multiplexing eMBB and URLLC services on the same RAN is particularly challenging, which has motivated some recent works.
In [2], the sum rate of the eMBB, and URLLC, is optimized by ensuring that each user's traffic load demand is met and the slice isolation is guaranteed, thus promoting an amicable service coexistence.
In [18], a RAN slicing is considered in a coordinated multipoint system to guarantee the QoS requirements of eMBB and URLLC services. Moreover, [19] investigates the minimization of the system's power for the  RAN slicing of eMBB and URLLC downlink services using non-orthogonal multiple access techniques.
In  [5], the problem of resource allocation for the coexistence of eMBB and URLLC services is formulated and solved by deep reinforcement learning.
% In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services. The system guarantees latency, service rate, and reliability maintenance.

In [9], [20], the authors address the issue of beamforming and VMs activation (using virtualization) in a C-RAN system with limited fronthaul capacity.
Paper [9] aims to minimize the energy cost with the system delay, fronthaul capacity, and rate constraint.
Also, transmission and processing delays are modeled based on M/M/1 queueing theory to guarantee UE delays.
In  [21], [22], the problem of joint virtual computing resource allocation with beamforming is formulated. Also, the association of RRH to the UE is considered and solved using innovative methods.

In  [23],[24], the problem of joint power allocation and RRH association in a H-CRAN system is considered to maximize the energy efficiency.
Finally, in [25], the optimum power is obtained in the massive MIMO aided C-RAN system, and the problem of RRH to BBU and RRH to UE association is formulated and solved.
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment6:} `` Regarding the Reviewer’s comment with respect to the network slice management, whereas the authors have introduced the 4 stages of the life cycle of a network slice, the connection to their approach is very vague. It is still not clear how this process is achieved and how it is linked to their method. I was expecting at least a connection or introduction to Fig.1 where the system is shown. Additionally, more information with respect to the interaction with the system would have been required in that regard. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We thank the reviewer for the given remark. We modified and clarified the description of the life cycle of a network slice. We report the relation between Fig. 1 and the network slice management and explain more about our algorithm in Section V-B and report it as follows.

@@

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment7:} ``With respect to the convergence time of the algorithm, the Reviewer had made a suggestion to the authors to include it in the current version of the manuscript, yet the authors do not seem to have done that. The authors’ response points to Fig. 11. However if one looks at Fig.11 carefully, understands that only the Aggregate throughput is shown there. Even if one considers the Section III-C1 and III-C2 that the authors demonstrate as their convergence analysis and proof, there is no evidence or clarification of any delay value with respect to their algorithm’s convergence. On the one hand it is very beneficial to have a mathematical proof that the algorithm converges. On the other hand, it is equally important to portray these findings with numerical values. In any case, this is not applicable in the current version of the manuscript. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We apologize for wrongly responding to this comment in the previous version of the response letter.
Based on this comment, we added Fig. 11 and Table III to our manuscript.
To be sure that we consider the reviewer's concern, we added two different numerical results. In Figure 11, the mean total delay of the URLLC service is illustrated versus the number of iterations, and the convergence of the proposed algorithm is shown. In Table III, the execution delay time of the algorithm is reported versus the different number of UEs. It shows the effect of the number of UEs on the execution time.
Below, we reported these changes.

@@

In Fig. 11,  the mean total delay is indicated according to the number of iterations. In Table III, we reported the execution delay time according to the number of UEs in the system to investigate the full consideration of the reviewer.

In Fig. \ref{fig:2}, the mean total delay time of URLLC service is indicated according to the number of iterations of the
proposed algorithm (IABV) for different numbers of UEs for one service. This figure shows that the algorithm converged to the fixed value after four iterations.
\begin{figure}[H]
  \centering
    \includegraphics[scale = 0.5]{iterD.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Mean Total Delay (usec) vs. Number of iterations}
  \label{fig:2}
\end{figure}

@@

Table III shows the execution delay time versus the number of UEs for one service. We run our simulation on the system with configures (RAM = 8 GB, CPU = Core i5, SSD Hard Disk). 
 As the number of UEs in the system increases, the execution time increases polynomially. 
Moreover, we added Fig. \ref{fig:3} to the response letter, which is equal to Table III, but for space reasons, we reported Table III instead of Fig. \ref{fig:3}.
\begin{figure}[H]
  \centering
    \includegraphics[scale = 0.5]{exec.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Execution Time vs. Number of UEs}
  \label{fig:3}
\end{figure}

\begin{table}[H]
\captionsetup{labelformat=empty}
 \caption {Table(III) Execution Time vs. Number of UEs} 
\begin{center}
 \scalebox{0.9}{
\begin{tabular}{|| l || l| l |l |l |l ||}
 \hline
Number of UEs & 5 & 10 & 15 & 20 & 25 \\ 
Execution Time (usec)& 12.156 & 19.156 &  29.140 & 44.573 & 67.912 \\
 \hline
\end{tabular}}
\end{center}
\end{table}

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment8:} `As a final remark, the structure of the paper needs major re-construction. Several Sections are very lengthy and could be reduced while creating additional Sections. In the current format it is very hard to follow. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
Thank you for this comment to make our paper more readable. We modified the entire paper based on this comment.
We updated the manuscript while creating additional Sections such as "background" and "related literature" Sections. Moreover, we modified and shortened the unnecessary paragraphs, for instance, in the "introduction," "system model," "proposed algorithm," and "numerical results." Our paper was modified totally to satisfy the reviewer's concerns.

@@

     UPF &  user plane function \\ [.5ex]

  UE &  user equipment \\ [.5ex]
  SINR & signal-to-noise-plus-interference ratio \\ [.5ex]
  CAPEX & capital expenditures  \\ [.5ex]
  OPEX & operating expenses  \\ [.5ex]

  KKT &  Karush-Kuhn-Tucker \\ [.5ex]
 \toprule
 \end{tabular}}
 \end{center}
 \end{table}

### 2022-07-14 Journal1/Response3/Response.tex

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment11:} `Finally, the figures in the current version of the manuscript are very small and extremely hard to read. Therefore, re-formatting is necessary. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We modified all figures to make them more readable due to this comment. We enlarge the texts of the figures, bold the lines, and markers, re-format all the figures, and place them in sub-figures to improve their presentation.

\clearpage
\noindent
\begin{longtable}{|p{.975\textwidth}|}
\hline \hline %\hline \hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Reviewer 3} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent Comments to the Author} ``
The reviewer has addressed most of the comments satisfactorily. However, the paper still contains some minor issues as follows ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We are pleased to thank the reviewer for his/her detailed and thorough reading of this manuscript. We hope the responses provided here will assist the reviewer in relieving his/her concerns.

@@

     UPF &  user plane function \\ [.5ex]

  UE &  user equipment \\ [.5ex]
  SINR & signal-to-noise-plus-interference ratio \\ [.5ex]
  CAPEX & capital expenditures  \\ [.5ex]
  OPEX & operating expenses  \\ [.5ex]

  KKT &  Karush-Kuhn-Tucker \\ [.5ex]
 \toprule
 \end{tabular}}
 \end{center}
 \end{table}
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment2:} ``Eq. (3) includes inter-slice interference but a sentence following the equation mentions that there is no inter-slice interference because slices are isolated, which is confusing''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\} 
We thank the reviewer for reporting this ambiguity.
We revised this section and rewrote equation (3) by removing the inter-slice interference to clarify this equation. Moreover, we removed two figures of Fig. 2 and Fig. 3 since they don't add much to what is already written in words after revision, and even after this revision, Fig. 2 makes the paper vaguer. We also aim for a more concise manuscript.
Below we report the revised sentences.

Network slicing techniques significantly reduce inter-service (inter-slice) interference.
One way to leverage a two-time scale PRB scheduling is to isolate PRBs in slices (in the first time scale) and schedule the PRBs to the UEs of the slices (in the second time scale). Another method consists of allocating part of the PRBs of eMBB services to URLLC and mMTC [2], [5], [32]. In this paper, we assume that the PRB scheduling is performed. Also, in Section V-A, we briefly study the PRB scheduling between slices.
Since there are limited resources, inter-service interference cannot be eliminated entirely. Nevertheless, isolating the slices reduces inter-service interference considerably and allows us to ignore it mathematically.
Back to (2), $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise, and can be represented as 
%{\color{red} use paranthesis in the following equation to clear +}
%\begin{subequations}\label{eqI}
%\begin{alignat}{4}
%\begin{align}\label{eqI}
%&I_{r,u(s,i)}^{k} =\nonumber\\
% &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\nonumber\\
%&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\nonumber\\
%&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
%\end{align}
%\end{alignat}
%\end{subequations}
%{\color{red} $\gamma_1$ is constant used instead of variable. }
\begin{align}\label{eqI}
&I_{r,u(s,i)}^{k} =+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}}\nonumber\\
 &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}},
\end{align}
%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
where $e^{k}_{u(s,i)}$ is a binary variable that indicates whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU, or not. %($\gamma_1$ and $\gamma_2$ are two variales. You  define on variable here.)
Furthermore, there is no inter-slice interference, only intra-slice interference, since slices are assumed to be isolated. 
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment3:} ``The captions of Figs. 9, 12 and 14 are incomplete.''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}  
Thank you for this comment. We checked and corrected all the figure's captions. As part of our efforts to make all figures more readable, we grouped them into sub-figures and reformatted them to give them more attractive appearance.
